Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-07-27 submission/manuscript.Rmd
fix formatting

```
Katherine M. Bonefas, Ilakkiya Venkatachalam, and Shigeki Iwase. 
# Abstract

@@

```
### Germline genes are misexpressed in the _Kdm5c_-KO brain
- Intriguingly, some of the ectopic testis transcripts identified within the _Kdm5c_-KO hippocampus have known functions unique to germ cells[@scandagliaLossKdm5cCauses2017], suggesting KDM5C may play a role in demarcating somatic versus germline identity.

>>>>

```
Katherine M. Bonefas, Ilakkiya Venkatachalam, and Shigeki Iwase.

# Abstract

@@

```
### Germline genes are misexpressed in the _Kdm5c_-KO brain
